R for Clinical Study Reports and Submission

### 2021-11-17 tlf-overview.Rmd

> FDA's PDF specification is a general reference. Each organization can define
> more specific TLF format requirements that can be different from the examples in this book.

@@

@@

There are other R packages that can create TLFs in `.rtf` or `.docx` format.
Interested readers can refer "Microsoft/LibreOffice Formats" section in
[CRAN Task View: Reproducible Research](https://cran.r-project.org/web/views/ReproducibleResearch.html)
for an overview.

>>>>

::: {.rmdnote}
FDA's PDF specification is a general reference. Each organization can define
more specific TLF format requirements that can be different from the examples in this book.
:::

@@

::: {.rmdnote}
There are other R packages to create TLFs in ASCIII, RTF and Word format.
For example, `rtables`, `huxtable`, `pharmaRTF`, `gt`, `officer`, `flextable` etc.
Here we focus on `r2rtf` to illustrate the concept.  
Reader is encourage to explore other R packages to find the proper tools to fit your purpose. 
:::

@@
